\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 08-That's...?}
\subsection{Quiz}
\begin{enumerate}
  \color{red} \item 내가 하기 싫으니까
    \color{light-gray} That's because I don't want to.
  \color{red} \item 그래서 내가 행복한 거야.
    \color{light-gray} That's why I'm happy.
  \color{red} \item 내가 물어본 게 그거야.
    \color{light-gray} That's what I asked.
  \color{red} \item 내가 들은 건 그게 아니야.
    \color{light-gray} That's not what I heard.
  \color{red} \item 그게 이 문제를 푸는 방법이야.
    \color{light-gray} That's how you solve this problem.
  \color{red} \item 내가 사랑에 빠진 게 그때야.
    \color{light-gray} That's when I fell in love.
   \color{red} \item 내가 그녀를 본 게 거기야.
    \color{light-gray} That's where I saw her.
\end{enumerate}

\subsection{Pattern 051 - That's because... 그건 \texttildelow 때문이야 / \texttildelow 하니까}
\begin{itemize}
  \item \textbf{That's because} he doesn't know anything.
  \item \textbf{That's because} I don't feel like it.
  \item \textbf{That's because} I don't get it.
  \item \textbf{That's because} he flunked the test.(flunk: 낙제하다. 시험에서 떨어지다.)
  \item \textbf{That's because} Minji broke his heart.
\end{itemize}

\subsection{Pattern 052 - That's why... 그래서 \texttildelow 한 거야}
\begin{itemize}
  \item \textbf{That's why} I'm worried.
  \item \textbf{That's why} I'm leaving.
  \item \textbf{That's why} I dumped her.
  \item \textbf{That's why} I gave up.
  \item \textbf{That's why} I'm grounded.
\end{itemize}

\subsection{Pattern 053 - That's what... \texttildelow 이 그거야}
\begin{itemize}
  \item \textbf{That's what} I'm saying.
  \item \textbf{That's what} I told her.
  \item \textbf{That's what} I told him to do.
  \item \textbf{That's what} I bought yesterday.
  \item \textbf{That's what} I thought.
\end{itemize}

\subsection{Pattern 054 - That's not what... \texttildelow 한 건 그게 아니야}
\begin{itemize}
  \item \textbf{That's now what} I meant.
  \item \textbf{That's now what} I was looking for.
  \item \textbf{That's now what} I asked for.
  \item \textbf{That's now what} Simon said.
  \item \textbf{That's now what} I saw on the website.
\end{itemize}

\subsection{Pattern 055 - That's how... 그게 \texttildelow 하는 방법[방식]이야 / \texttildelow 이 그런 거야}
\begin{itemize}
  \item \textbf{That's how} he wants it done.
  \item \textbf{That's how} Sejoon does it.
  \item \textbf{That's how} I spend my spare time.
  \item \textbf{That's how} you bake banana muffins.
  \item \textbf{That's how} life goes.
\end{itemize}

\subsection{Pattern 056 - That's when... 그때 \texttildelow 했어 / \texttildelow 한 게 그때야}
\begin{itemize}
  \item \textbf{That's when} I fell in love with Yoonji.
  \item \textbf{That's when} I remembered.
  \item \textbf{That's when} they started fighting.
  \item \textbf{That's when} he started smoking.
  \item \textbf{That's when} I started my own business.
\end{itemize}

\subsection{Pattern 057 - That's where... 그곳에서 \texttildelow 했어 / \texttildelow 한 게 거기야}
\begin{itemize}
  \item \textbf{That's where} I last saw my bag.
  \item \textbf{That's where} I first met her.
  \item \textbf{That's where} I took my TOEFL.
  \item \textbf{That's where} I'm headed too.(내가 가는 곳도 거기야.)
  \item \textbf{That's where} you're wrong.(거기서 네가 틀린 거야.)
\end{itemize}

\end{document}
