\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 16-다양한 감정 표현하기}
\subsection{Quiz}
\begin{enumerate}
  \color{red} \item 진심을 알고 충격이었어.
    \color{light-gray} I was shocked to know the truth.
  \color{red} \item 난 기꺼이 널 도와줄 용의가 있어.
    \color{light-gray} I'm willing to help you.
  \color{red} \item 데이트 때문에 긴장돼.
    \color{light-gray} I'm nervous about my date.
  \color{red} \item 내 남자 친구 때문에 속상해.
    \color{light-gray} I'm upset about my boyfriend.
  \color{red} \item 나 완전 피곤해.
    \color{light-gray} I'm totally tired.
  \color{red} \item 이거 완전 멋져.
    \color{light-gray} This is totally cool.
   \color{red} \item 나 좀 졸려.
    \color{light-gray} I'm kind of sleepy.
   \color{red} \item 나 밖에 나갈 기분이 아니야.
    \color{light-gray} I don't feel like going out.
\end{enumerate}

\subsection{Pattern 108 - I was shocked to ... \texttildelow 하다니 충격이었어}
\begin{itemize}
  \item \textbf{I was shocked to} hear the news.
  \item \textbf{I was shocked to} find him there.
  \item \textbf{I was shocked to} know the truth.
  \item \textbf{I was shocked to} find that he is only 30.
  \item \textbf{I was shocked to} see him with another woman.
\end{itemize}

\subsection{Pattern 109 - I'm willing to ... 난 기꺼이  \texttildelow 할 용의가 있어/각오가 돼 있어}
\begin{itemize}
  \item \textbf{I'm willing to} take risks.
  \item \textbf{I'm willing to} work for him.
  \item \textbf{I'm willing to} do anything for her.
  \item \textbf{I'm willing to} think about it.
  \item \textbf{I'm willing to} get my hands dirty.(get one's hands dirty: 손을 더럽히다, 불법 행위를 하다)
\end{itemize}

\subsection{Pattern 110 - I'm nervous about... \texttildelow 때문에 긴장돼/떨려}
\begin{itemize}
  \item \textbf{I'm nervous about} my test results.
  \item \textbf{I'm nervous about} my first day of work.
  \item \textbf{I'm nervous about} my audition this afternoon.
  \item \textbf{I'm so nervous about} my job interview.
  \item \textbf{I'm a little nervous about} my blind date.
\end{itemize}

\subsection{Pattern 111 - I'm upset about ... \texttildelow 때문에 속상해}
\begin{itemize}
  \item \textbf{I'm upset about} his attitude.
  \item \textbf{I'm upset about} my best friend.
  \item \textbf{I'm upset about} the fight I had with him.
  \item \textbf{I'm upset about} getting ripped off.(rip off: 바가지 씌우다)
  \item \textbf{I'm upset about} not getting the best grade in my class.
\end{itemize}

\subsection{Pattern 112 - I'm totally ... 나 완전히 \texttildelow 해}
\begin{itemize}
  \item \textbf{I'm totally} excited.
  \item \textbf{I'm totally} embarrassed.
  \item \textbf{I'm totally} confused.
  \item \textbf{I'm totally} bored.
  \item \textbf{I'm totally} against it.
\end{itemize}

\subsection{Pattern 113 - This is totally ... 이거 완전히 \texttildelow 해}
\begin{itemize}
  \item \textbf{This is totally} awesome.
  \item \textbf{This is totally} weird.(기묘한, 이상한  [wiərd])
  \item \textbf{This is totally} unnecessary.
  \item \textbf{This is totally} crappy.(crappy: 형편없는, 후진(회화체))
  \item \textbf{This is totally} unacceptable.
\end{itemize}

\subsection{Pattern 114 - I'm kind of ... 나 좀 \texttildelow 해}
\begin{itemize}
  \item \textbf{I'm kind of} depressed.
  \item \textbf{I'm kind of} offended by that.
  \item \textbf{I'm kind of} busy at the moment.
  \item \textbf{I'm kind of} tied up now.
  \item \textbf{I'm kind of} nervous.
\end{itemize}

\subsection{Pattern 115 - I don't feel like ... 나 \texttildelow 이 안 내켜 / 나 \texttildelow 할 기분이 아니야}
\begin{itemize}
  \item \textbf{I don't feel like} going out tonight.
  \item \textbf{I don't feel like} doing anything.
  \item \textbf{I don't feel like} cooking.
  \item \textbf{I don't feel like} eating right now.
  \item \textbf{I don't feel like} company tonight.(company: 누구와 함께 있는 것)
\end{itemize}

\end{document}
