\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 12-When\&Where}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 너 언제 왔어?
    \color{light-gray} When did you come?
  \color{red} \item 너 언제 떠날거야?
    \color{light-gray} When are you leaving?
  \color{red} \item 우리가 마지막으로 얘기한 게 언제였지?
    \color{light-gray} When was the last time we talked?
  \color{red} \item 네가 언제부터 신경 쓰는 건데?
    \color{light-gray} Since when do you care?
  \color{black} \item 남자 화장실이 어디 있죠?
    \color{light-gray} Where is the men's room?
  \color{red} \item 어디로 연락하면 되나요?
    \color{light-gray} Where can I reach you?
   \color{black} \item 너 그거 어디서 샀어?
    \color{light-gray} Where did you get it?
\end{enumerate}

\subsection{Pattern 079 - When did you...?}
\begin{itemize}
  \item \textbf{When did you} get here?
  \item \textbf{When did you} call me?
  \item \textbf{When did you} move?
  \item \textbf{When did you} go to bed?
  \item \textbf{When did you} switch job?
\end{itemize}

\subsection{Pattern 080 - When are you -ing? 언제 \texttildelow 할 거야?}
When are you going to ...? 
When dod you plan to ...?
When will you ...?

\begin{itemize}
  \item \textbf{When are you} leav\textbf{ing}?
  \item \textbf{When are you} com\textbf{ing} back?
  \item \textbf{When are you} get\textbf{ting} married?
  \item \textbf{When are you} tal\textbf{king} the TOEIC?
  \item \textbf{When are you} get\textbf{ting} off work today?
\end{itemize}

\subsection{Pattern 081 - When was the last time ...? 마지막으로 \texttildelow 한 게 언제야?}
\begin{itemize}
  \item \textbf{When was the last time} you saw him?
  \item \textbf{When was the last time} you read a book?
  \item \textbf{When was the last time} we talked?
  \item \textbf{When was the last time} you heard from him?
  \item \textbf{When was the last time} you went shopping?
\end{itemize}

\subsection{Pattern 082 - Since when do you ...? 네가 언제부터 \texttildelow 하는 건데?}
\begin{itemize}
  \item \textbf{Since when do you} care?
  \item \textbf{Since when do you} play golf?
  \item \textbf{Since when do you} ask for my permission?
  \item \textbf{Since when did you} listen to me?
  \item \textbf{Since when did you} care about my feelings?
\end{itemize}

\subsection{Pattern 083 - Where is...? \texttildelow 는 어디 있나요?}
\begin{itemize}
  \item \textbf{Where is} Caroline?
  \item \textbf{Where is} the line?(어디에서 줄 서면 되나요?)
  \item \textbf{Where is} the gas station?
  \item \textbf{Where is} the subway station?
  \item \textbf{Where is} the nearest convenience store?(convenience store: 편의점)
\end{itemize}

\subsection{Pattern 084 - Where can I...? 어디서 \texttildelow 할 수 있나요? / 어디에 \texttildelow 하면 되나요?}
\begin{itemize}
  \item \textbf{Where can I} reach you?(어디로 연락하면 되나요?
  \item \textbf{Where can I} see you?
  \item \textbf{Where can I} buy tickets?
  \item \textbf{Where can I} apply?
  \item \textbf{Where can I} find the ladies' room?
\end{itemize}

\subsection{Pattern 085 - Where did you...? 어디서 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{Where did you} read that? 
  \item \textbf{Where did you} hear that?
  \item \textbf{Where did you} get your eyes done?(눈 수술 어디서 했어?)(get one's eyes done: 눈 수술을 하다)
  \item \textbf{Where did you} get your haircut?
  \item \textbf{Where did you} get it?
\end{itemize}

\end{document}
