\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 09-There is...}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 시간이 없어. 
    \color{light-gray} There is no time.
  \color{black} \item 할 게 아무것도 없어. 
    \color{light-gray} There is nothing to do.
  \color{red} \item 실수가 있는 것 같습니다. 
    \color{light-gray} There seems to be a mistake.
  \color{red} \item 내가 그걸 할 수 있을 리가 없어.
    \color{light-gray} There's no way (that) I can do it.
  \color{red} \item 분명히 방법이 있을 거야. 
    \color{light-gray} There must be a way.
  \color{red} \item 항상 희망이 있잖아.
    \color{light-gray} There is always hope.
   \color{red} \item 방법이 있나요?
    \color{light-gray} Is there any way?
\end{enumerate}

\subsection{Pattern 058 - There's no... \texttildelow 이 없어}
\begin{itemize}
  \item \textbf{There's no} time for that.
  \item \textbf{There's no} time to change clothes.
  \item \textbf{There's no} answer.
  \item \textbf{There's no} way out.
  \item \textbf{There's no} reason to believe you.
\end{itemize}

\subsection{Pattern 059 - There's nothing + 형용사/부정사 \texttildelow 한/\texttildelow 할 것이 아무것도 없어}
\begin{itemize}
  \item \textbf{There's nothing} wrong.
  \item \textbf{There's nothing} weird about it.
  \item \textbf{There's nothing} new in your report.
  \item \textbf{There's nothing} to lose.
  \item \textbf{There's nothing} to stop me.
\end{itemize}

\subsection{Pattern 060 - There seems to be... \texttildelow 이 있는 것 같아}
\begin{itemize}
  \item \textbf{There seems to be} a problem.
  \item \textbf{There seems to be} a mistake here.
  \item \textbf{There seems to be} a misunderstanding.
  \item \textbf{There seems to be} something wrong.
  \item \textbf{There seems to be} a disagreement.
\end{itemize}

\subsection{Pattern 061 - There's no way (that)... \texttildelow 일 리가 없어}
\begin{itemize}
  \item \textbf{There's no way} he did better than me.
  \item \textbf{There's no way} the professor will agree.
  \item \textbf{There's no way} he's telling the truth.
  \item \textbf{There's no way} I can do that.
  \item \textbf{There's no way} he'll win the trial.(그가 재판에 이길 리가 없어.)
\end{itemize}

\subsection{Pattern 062 - There must be... 분명히 \texttildelow 이 있을 거야 / \texttildelow 한 게 틀림없어}
\begin{itemize}
  \item \textbf{There must be} a way.
  \item \textbf{There must be} a better way.
  \item \textbf{There must be} a reason.
  \item \textbf{There must be} something between them.
  \item \textbf{There must be} something wrong with him.
\end{itemize}

\subsection{Pattern 063 - There's always... 항상 \texttildelow 이 있잖아 / 항상 \texttildelow 은 있게 마련이야}
\begin{itemize}
  \item \textbf{There's always} hope.(항상 희망이 있잖아.)
  \item \textbf{There's always} next time.
  \item \textbf{There's always} a way out.
  \item \textbf{There's always} tomorrow.
  \item \textbf{There's always} an excuse with you.(너한텐 항상 핑곗거리가 있더라.)
\end{itemize}

\subsection{Pattern 064 - Is there any...? \texttildelow 이 있나요?}
\begin{itemize}
  \item \textbf{Is there any} soy sauce left?
  \item \textbf{Is there any}thing I can do for you?
  \item \textbf{Is there any}one who can help me?
  \item \textbf{Is there any}thing good on TV?
  \item \textbf{Is there any} reason I should believe you?
\end{itemize}

\end{document}
