\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 15-How + 형용사/부사}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 이거 얼마에요?
    \color{light-gray} How much is it?
  \color{red} \item 얼마나 자주 외식해?
    \color{light-gray} How often eat out?
  \color{red} \item 여기에 얼마나 빨리 올 수 있어?
    \color{light-gray} How soon can you get here?
  \color{black} \item 여기에서 산 지 얼마나 오래됐어?
    \color{light-gray} How long have you lived here?
  \color{black} \item 이거 고치는 데에 얼마나 걸려요?
    \color{light-gray} How does it take to fix this?
  \color{black} \item 술 몇 잔 마셨어?
    \color{light-gray} How many drinks did you have?  
  \color{black} \item 시간을 얼마만큼 썼어?
    \color{light-gray} How much time did you spend?
\end{enumerate}

\subsection{Pattern 101 - How much is...? \texttildelow 이 얼마에요?}
\begin{itemize}
  \item \textbf{How much is} the iPad?
  \item \textbf{How much is} the gym membership?
  \item \textbf{How much is} a haircut here?
  \item \textbf{How much is} the bus fare?
  \item \textbf{How much is} a round-trip ticket?
\end{itemize}

\subsection{Pattern 102 - How often do you...? 얼마나 자주 \texttildelow 해?}
\begin{itemize}
  \item \textbf{How often do you} eat out?(eat out: 외식하다)
  \item \textbf{How often do you} go to the movies?
  \item \textbf{How often do you} exercise?
  \item \textbf{How often do you} tweet?
  \item \textbf{How often do you} go to the gym?
\end{itemize}

\subsection{Pattern 103 - How soon can...? 얼마나 빨리 \texttildelow 할 수 있나요?}
\begin{itemize}
  \item \textbf{How soon can} you get here?
  \item \textbf{How soon can} I get it back?
  \item \textbf{How soon can} you get off work?(get off work: 퇴근하다)
  \item \textbf{How soon can} you deliver my order?
  \item \textbf{How soon can} you have it on my desk?
\end{itemize}

\subsection{Pattern 104 - How long have you p.p.? \texttildelow 한 지 얼마나 오래됐어?}
\begin{itemize}
  \item \textbf{How long have you lived} here?
  \item \textbf{How long have you been} with him?(사귄지 얼마나 됐어?)
  \item \textbf{How long have you been} separated?(separated: 헤어진, 별거 중인)
  \item \textbf{How long have you worked} there?
  \item \textbf{How long have you been} in Korea?
\end{itemize}

\subsection{Pattern 105 - How long does it take to ...? \texttildelow 하는 데에 얼마나 걸려요?}
\begin{itemize}
  \item \textbf{How long does it take to} get there?
  \item \textbf{How long does it take to} get to work?(get to work: 출근하다)
  \item \textbf{How long does it take to} edit the photo?
  \item \textbf{How long does it take to} finish this?
  \item \textbf{How long does it take} (for) you \textbf{to} get dressed?(get dressed: 옷 입다)
\end{itemize}

\subsection{Pattern 106 - How many + 명사...? 몇 개를 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{How many} drinks did you have?
  \item \textbf{How many} books did you buy?
  \item \textbf{How many} people came to the party?
  \item \textbf{How many} counties have you been to?
  \item \textbf{How many} followers do you have on Twitter?
\end{itemize}

\subsection{Pattern 107 - How much + 명사...? 얼마만큼 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{How much} help did you get?
  \item \textbf{How much} money do you have now?
  \item \textbf{How much} sleep did you get?
  \item \textbf{How much} time did you spend on the computer?
  \item \textbf{How much} coffee do you drink every day?
\end{itemize}

\end{document}
