\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 04-I can't...}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 걔를 더 이상 못 참겠어
    \color{light-gray} I can't stand him anymore.
  \color{black} \item 노래 부르는 것을 멈출 수 가 없어.
    \color{light-gray} I can't stop siging
  \color{black} \item 네가 농담하는 건지 아닌지 모르겠어.
    \color{light-gray} I can't tell if you're joking.
  \color{black} \item 걔가 결혼했다니 안 믿어져.
    \color{light-gray} I can't believe (that) she's married.
  \color{black} \item 왜 네가 걔를 좋아하는지 이해가 안 돼.
    \color{light-gray} I can't understand why you like her.
  \color{black} \item 그거 나중에 하면 안 돼?
    \color{light-gray} Can't I do it later?
  \color{black} \item 기다릴 수 없어?
    \color{light-gray} Can't you wait?
  \color{black} \item 계속 걔를 피할 순 없는 거잖아.
    \color{light-gray} You can't keep avoiding him.
\end{enumerate}

\subsection{Pattern 024 - I can't stand... \texttildelow 을 못 참겠어}
\begin{itemize}
  \item \textbf{I can't stand} your lies.
  \item \textbf{I can't stand} this song.
  \item \textbf{I can't stand} my sister.
  \item \textbf{I can't stand} being around him.(그와 같이 있는 거 못 참겠어.)
  \item \textbf{I can't stand} working with her.
\end{itemize}

\subsection{Pattern 025 - I can't stop -ing \texttildelow 을 멈출 수가 없어}
\begin{itemize}
  \item \textbf{I can't stop} think\textbf{ing} bout you.
  \item \textbf{I can't stop} worry\textbf{ing}
  \item \textbf{I can't stop} lov\textbf{ing} you.
  \item \textbf{I can't stop} cry\textbf{ing}.
  \item \textbf{I can't stop} watch\textbf{ing} Prison Break.
\end{itemize}

\subsection{Pattern 026 - I can't tell if... \texttildelow 인지 아닌지 모르겠어}
\begin{itemize}
  \item \textbf{I can't tell if} he's cheating on me.(그가 바람피우는 건지 아닌지 모르겠어.)
  \item \textbf{I can't tell if} you're joking.
  \item \textbf{I can't tell if} she has feelings for me.(그녀가 날 좋아하는 건지 아닌지 모르겠어.)
  \item \textbf{I can't tell if} that was a compliment.(그게 칭찬이었는지)
  \item \textbf{I can't tell if} you did that on purpose.(on purpose: 고의로, 의도적으로)
\end{itemize}

\subsection{Pattern 027 - I can't believe (that)... \texttildelow 라니 안 믿어져}
\begin{itemize}
  \item \textbf{I can't believe (that)} she's married.
  \item \textbf{I can't believe (that)} you're still here.
  \item \textbf{I can't believe} it's already 11.
  \item \textbf{I can't believe} you cheated on the exam.
  \item \textbf{I can't believe} you fell for that.
\end{itemize}

\subsection{Pattern 028 - I can't understand why... 왜 \texttildelow 인지 이해가 안 돼}
\begin{itemize}
  \item \textbf{I can't understand why} you don't listen.
  \item \textbf{I can't understand why} he's not here.
  \item \textbf{I can't understand why} I got this wrong.(왜 이걸 틀린 건지 이해가 안 돼, get \texttildelow wrong: \texttildelow 을 잘못 생각하다, 오해하다)
  \item \textbf{I can't understand why} you're confused.
  \item \textbf{I can't understand why} you like her.
\end{itemize}

\subsection{Pattern 029 - Can't I...? \texttildelow 하면 안 돼?}
\begin{itemize}
  \item \textbf{Can't I} read it tomorrow?
  \item \textbf{Can't I} go with you?
  \item \textbf{Can't I} just text you tonight?
  \item \textbf{Can't I} hand it in a day later?
  \item \textbf{Can't I} just pay you back later?
\end{itemize}

\subsection{Pattern 030 - Can't you...? \texttildelow 을 할 수 없어? / \texttildelow 을 하면 안 돼?}
\begin{itemize}
  \item \textbf{Can't you} call me back later?
  \item \textbf{Can't you} give me another chance?
  \item \textbf{Can't you} be honest?
  \item \textbf{Can't you} focus?
  \item \textbf{Can't you} wait till tomorrow?
\end{itemize}

\subsection{Pattern 031 - You can't keep -ing 계속 \texttildelow 할 순 없는 거잖아}
\begin{itemize}
  \item \textbf{You can't keep} avoid\textbf{ing} him.
  \item \textbf{You can't keep} skipp\textbf{ing} class.
  \item \textbf{You can't keep} mak\textbf{ing} up excuses.(계속 핑곗거리를 만들 순 없잖아.)
  \item \textbf{You can't keep} ly\textbf{ing} to yourself.(계속 네 스스로를 속일 순 없잖아.)
  \item \textbf{You can't keep} ignor\textbf{ing} his texts.
\end{itemize}

\end{document}
