\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 05-Don't...}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 나한테 전화하는 거 잊지 마.
    \color{light-gray} Don't forget to call me.
  \color{black} \item 바보 같이 굴지 좀 마.
    \color{light-gray} Don't be stupid(dumb).
  \color{black} \item 잠잘 생각도 하지 마.
    \color{light-gray} Don't even think about sleeping.
  \color{black} \item 너 숙제 있는 거 아냐?
    \color{light-gray} Don't you have your homework?
  \color{black} \item 생각해 봐야 하는 거 아니야?
    \color{light-gray} Don't you think you should think about it?
  \color{black} \item 설마 잊어버렸다는 건 아니겠지?
    \color{light-gray} Don't tell me (that) you forgot.
  \color{black} \item 넌 나한테 인사도 안 하더라.
    \color{light-gray} You don't say hi to me.
\end{enumerate}

\subsection{Pattern 032 - Don't forget to... \texttildelow 하는 거 잊지 마}
\begin{itemize}
  \item \textbf{Don't forget to} text me later.
  \item \textbf{Don't forget to} leave the door open.
  \item \textbf{Don't forget to} buy the tickets today.
  \item \textbf{Don't forget to} say hello to him for me.(나 대신 걔한테 안부 전하는 거 잊지 마.)
  \item \textbf{Don't forget to} give me back my notes.
\end{itemize}

\subsection{Pattern 033 - Don't be... \texttildelow 하게 굴지 좀 마}
\begin{itemize}
  \item \textbf{Don't be} mean.(못되게 굴지 마.)
  \item \textbf{Don't be} a baby.(아기같이 굴지 좀 마.)
  \item \textbf{Don't be} dumb.
  \item \textbf{Don't be} so pretty.(그렇게 쩨쩨하게 굴지 좀 마.)
  \item \textbf{Don't be} so cheap.(치사하게 굴지 마.)
\end{itemize}

\subsection{Pattern 034 - Don't even think about... \texttildelow 할 생각도 하지 마}
\begin{itemize}
  \item \textbf{Don't even think about} it.
  \item \textbf{Don't even think about} sleeping tonight.
  \item \textbf{Don't even think about} complaining.
  \item \textbf{Don't even think about} speeding here.(여기선 과속할 생각도 하지 마.)
  \item \textbf{Don't even think about} talking back to him.(그분한텐 말대답할 생각도 하지마.)
\end{itemize}

\subsection{Pattern 035 - Don't you have...? 너 \texttildelow 있는 거 아냐? / 너 \texttildelow 없어?}
\begin{itemize}
  \item \textbf{Don't you have} homework today?
  \item \textbf{Don't you have} a dental appointment at 2?
  \item \textbf{Don't you have} a smartphone already?
  \item \textbf{Don't you have} any conscience?(너는 얌심도 없니?)
  \item \textbf{Don't you have} something better to do?(너 할 게 그렇게 없니?)
\end{itemize}

\subsection{Pattern 036 - Don't you think you should...? \texttildelow 해야 한다고 생각하지 않아? / \texttildelow 해야 하는 거 아니야?}
\begin{itemize}
  \item \textbf{Don't you think you should} tell me first?(나한테 먼저 말해야 한다고 생각 안 해?)
  \item \textbf{Don't you think you should} have a talk?(대화를 나눠야 되는 거 아니야?)
  \item \textbf{Don't you think you should} get going?
  \item \textbf{Don't you think you should}  do your work?
\end{itemize}

\subsection{Pattern 037 - Don't tell me (that)... 설마 \texttildelow 라는 건 아니겠지?}
\begin{itemize}
  \item \textbf{Don't tell me} you forgot all about it.(설마 그거 완전히 다 잊었다는 건 아니겠지?)
  \item \textbf{Don't tell me} you're tired already!
  \item \textbf{Don't tell me} you don't know.
  \item \textbf{Don't tell me} you slept in again.(설마 또 늦잠 잤다는 건 아니겠지?)
  \item \textbf{Don't tell me} you want to borrow money again.
\end{itemize}

\subsection{Pattern 038 - You don't... 넌 \texttildelow 안 하더라}
\begin{itemize}
  \item \textbf{You don't} say hi to me anymore.(넌 더 이상 나한테 인사도 안하더라)
  \item \textbf{You don't} say sorry first.
  \item \textbf{You don't} listen to other people.
  \item \textbf{You don't} call me.
  \item \textbf{You don't} say thank you to me now.
\end{itemize}

\end{document}
