\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 10-Who}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 넌 누구를 좋아해?
    \color{light-gray} Who do you like?
  \color{red} \item 누가 네 머리 해 줬어?
    \color{light-gray} Who did your hair?
  \color{red} \item 누가 운전할 거야?
    \color{light-gray} Who's gonna drive?
  \color{red} \item 또 누가 이거 봤어?
    \color{light-gray} Who else saw this?
  \color{red} \item 내가 거짓말 했다고 누가 그래?
    \color{light-gray} Who says (that) I lied?
  \color{red} \item 좀 다르면 어때?
    \color{light-gray} Who cares if you're different
   \color{red} \item 누가 그런 말을 하겠어?
    \color{light-gray} Who would say that?
\end{enumerate}

\subsection{Pattern 065 - Who do you...? 누구를 \texttildelow 해?}
\begin{itemize}
  \item \textbf{Who do you} like?
  \item \textbf{Who do you} support?
  \item \textbf{Who do you} agree with?
  \item \textbf{Who do you} trust more?
  \item \textbf{Who do you} resemble in your family?
\end{itemize}

\subsection{Pattern 066 - Who did...? 누가 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{Who did} your hair?
  \item \textbf{Who did} the best job?(누가 제일 잘했어?)
  \item \textbf{Who did} your make-up?
  \item \textbf{Who did} the decorations?
  \item \textbf{Who did} the illustrations in the brochure?(brochure: 소책자)
\end{itemize}

\subsection{Pattern 067 - Who's going to/gonna..? 누가 \texttildelow 할 거야?}
\begin{itemize}
  \item \textbf{Who's going to} drive?
  \item \textbf{Who's gonna} pay for dinner?
  \item \textbf{Who's gonna} train the dog?
  \item \textbf{Who's going to} replace James?
  \item \textbf{Who's gonna} bring the booze?(booze: 술)
\end{itemize}

\subsection{Pattern 068 - Who else...? 또 누가 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{Who else} saw this?(또 누가 이거 봤어?)
  \item \textbf{Who else} knows about this?
  \item \textbf{Who else} is available?
  \item \textbf{Who else} wants this?
  \item \textbf{Who else} wants to come?
\end{itemize}

\subsection{Pattern 069 - Who says (that)...? \texttildelow 라고 누가 그래?}
\begin{itemize}
  \item \textbf{Who says} I can't do it?(내가 못 한다고 누가 그래?)
  \item \textbf{Who says} I lied?(lie-lied-lied)
  \item \textbf{Who says} it's impossible?
  \item \textbf{Who says} I'm picky?(내가 까탈스럽다고 누가 그래?)
  \item \textbf{Who says} you can't be trusted?(널 믿을 수 없다고 누가 그래?)
\end{itemize}

\subsection{Pattern 070 - Who cares if...? \texttildelow 하면 뭐 어때? / 누가 \texttildelow 한지 상관해?}
\begin{itemize}
  \item \textbf{Who cares if} you're wrong?(틀리면 뭐 어때?)
  \item \textbf{Who cares if} he wins the game?
  \item \textbf{Who cares if} she's smarter?
  \item \textbf{Who cares if} you're a little different?
  \item \textbf{Who cares if} it's a bit unrealistic?
\end{itemize}

\subsection{Pattern 071 - Who would...? 누가 \texttildelow 하겠어}
\begin{itemize}
  \item \textbf{Who would} do something like that? (누가 그런 걸 하겠어?)
  \item \textbf{Who would} believe him?
  \item \textbf{Who would} talk like that?
  \item \textbf{Who would} hire someone like him?
  \item \textbf{Who would} do that to their own friend?(누가 자기 친구한테 그런 걸 하겠어?)
\end{itemize}

\end{document}
