\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 14-How}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 시험 어땠어?
    \color{light-gray} How was your test?
  \color{red} \item 거기 어떻게 가?
    \color{light-gray} How do I get there?
  \color{red} \item 너희는 어떻게 서로를 알아?
    \color{light-gray} How do you know each other?
  \color{red} \item 왜 나한테 말 안했어?
    \color{light-gray} How come you didn't tell me?
  \color{red} \item 내 새 머리에 대해 어떻게 생각해?
    \color{light-gray} How do you feel about my new hair?
  \color{black} \item 네가 어떻게 내 생일을 잊어버릴 수 있어?
    \color{light-gray} How could you forget my birthday?
   \color{red} \item 내가 그걸 어떻게 알아?
    \color{light-gray} How am I supposed to know that?
\end{enumerate}

\subsection{Pattern 094 - How was...? \texttildelow 어땠어?}
\begin{itemize}
  \item \textbf{How was} your date?
  \item \textbf{How was} the movie?
  \item \textbf{How was} your exam?
  \item \textbf{How was} your job interview?
  \item \textbf{How was} your trip to Italy?
\end{itemize}

\subsection{Pattern 095 - How do I...? 어떻게 \texttildelow 해?}
\begin{itemize}
  \item \textbf{How do I} download that?
  \item \textbf{How do I} get to your house?
  \item \textbf{How do I} solve this equation?
  \item \textbf{How do I} get to the Olympic Park?
  \item \textbf{How do I} turn on the air conditioner?
\end{itemize}

\subsection{Pattern 096 - How do you know...? 어떻게 \texttildelow 을 알아?}
\begin{itemize}
  \item \textbf{How do you know} her?
  \item \textbf{How do you know} each other?
  \item \textbf{How do you know} so much about computers?
  \item \textbf{How do you know} that she likes you?
  \item \textbf{How do you know} if it's true?
\end{itemize}

\subsection{Pattern 097 - How come...? 왜 \texttildelow 했어?}
\begin{itemize}
  \item \textbf{How come} you didn't tell me?
  \item \textbf{How come} you're so grumpy today?(grumpy: 짜증 내는)
  \item \textbf{How come} you're so nervous?
  \item \textbf{How come} you didn't call me?
  \item \textbf{How come} you didn't show up?
\end{itemize}

\subsection{Pattern 098 - How do you feel about...? \texttildelow 에 대해 어떻게 생각해?}
\begin{itemize}
  \item \textbf{How do you feel about} the new boss?
  \item \textbf{How do you feel about} my new hairstyle?
  \item \textbf{How do you feel about} the election results?
  \item \textbf{How do you feel about} capital punishment?(capital punishment: 사형 제도)
  \item \textbf{How do you feel about} working with him?
\end{itemize}

\subsection{Pattern 099 - How could you...? 네가 어떻게 \texttildelow 할 수 있어?}
\begin{itemize}
  \item \textbf{How could you} lie to me?
  \item \textbf{How could you} betray me like this?
  \item \textbf{How could you} talk back to your dad?
  \item \textbf{How could you} say something like that?
  \item \textbf{How could you} forget my birthday?
\end{itemize}

\subsection{Pattern 100 - How am I supposed to know...? 내가 \texttildelow 을 어떻게 알아?}
\begin{itemize}
  \item \textbf{How am I supposed to know}?
  \item \textbf{How am I supposed to know} the answer?
  \item \textbf{How am I supposed to know} the reason?
  \item \textbf{How am I supposed to know} why Jay lied?
  \item \textbf{How am I supposed to know} what he wants?
\end{itemize}

\end{document}
