\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 03-I'm going to...}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 난 걔를 용서할 거야.
    \color{light-gray} I'm going to forgive him.
  \color{black} \item 아무한테도 말하지 않을 거야.
    \color{light-gray} I'm not going to tell anymore.
  \color{black} \item 너 그거 살 거야?
    \color{light-gray} Are you going to buy that?
  \color{black} \item 너 나한테 말 안 할 거야?
    \color{light-gray} Aren't you going tell me?
  \color{black} \item 막 나가려던 참이었어.
    \color{light-gray} I was just gonna leave.
  \color{black} \item 그러려는 게 아니었는데(그럴 생각이 없었는데) 웃었어.
    \color{light-gray} I wasn't gonna, but I laughed.
  \color{black} \item 내가 이길 것 같아.
    \color{light-gray} I think I'm gonna win.
  \color{black} \item A를 못 받을 것 같아.
    \color{light-gray} I don't think I'm gonna get an A.
\end{enumerate}

\subsection{Pattern 016 - I'm going to/gonna... 난 \texttildelow 할거야}
\begin{itemize}
  \item \textbf{I'm going to} get a new laptop.
  \item \textbf{I'm going to} take a shower now.
  \item \textbf{I'm going to} tell her how I feel.
\end{itemize}

\subsection{Pattern 017 - I'm not going to/gonna... 난 \texttildelow하지 않을 거야/난 \texttildelow할 생각 없어}
\begin{itemize}
  \item \textbf{I'm not going to} do anything.
  \item \textbf{I'm not going to} forgive you this time.
  \item \textbf{I'm not going to} apologize to him.
\end{itemize}

\subsection{Pattern 018 - Are you going to/gonna...? 너 \texttildelow 할 거야?}
\begin{itemize}
  \item \textbf{Are you going to} tell him?
  \item \textbf{Are you going to} apply?
  \item \textbf{Are you} really \textbf{going to} buy that?
  \item \textbf{Are you gonna} tell on me?
\end{itemize}

\subsection{Pattern 019 - Aren't you going to/gonna...? 너 \texttildelow 안 할 거야?}
\begin{itemize}
  \item \textbf{Aren't you going to} tell him the truth?
  \item \textbf{Aren't you going to} apply for the job?
\end{itemize}

\subsection{Pattern 020 - I was just going to/gonna... 막 \texttildelow 하려던 참이었어}
\begin{itemize}
  \item \textbf{I was just gonna} say that.
  \item \textbf{I was just gonna} email it to you.
  \item \textbf{I was just going to} call you.
\end{itemize}

\subsection{Pattern 021 - I wasn't going to/gonna, but... 그러려는 게 아니었는데 \texttildelow / 그럴 생각이 없었는데 \texttildelow}
\begin{itemize}
  \item \textbf{I wasn't gonna, but} he insisted.(insist: 우기다)
  \item \textbf{I wasn't gonna, but} I bought another shirt.
  \item \textbf{I wasn't going to, but} I cried.
  \item \textbf{I wasn't going to, but} I called him.
\end{itemize}

\subsection{Pattern 022 - I think I'm going to/gonna... \texttildelow 할까 해 / \texttildelow 할 것 같아}
\begin{itemize}
  \item \textbf{I think I'm gonna} head to bed.
  \item \textbf{I think I'm} just \textbf{gonna} give up.
  \item \textbf{I think I'm gonna} fall in love with him.
  \item \textbf{I think I'm going to} throw up.(throw up: 토하다)
\end{itemize}

\subsection{Pattern 023 - I don't think I'm going to/gonna... \texttildelow 안 할까 해 / \texttildelow 못할 것 같아}
\begin{itemize}
  \item \textbf{I don't think I'm going to} win.
  \item \textbf{I don't think I'm gonna} make it on time.
  \item \textbf{I don't think I'm gonna} get an A.
\end{itemize}

\end{document}
