\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 02-I'm -ing}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 나 점점 추워져. 
    \color{light-gray} I'm getting cold.
  \color{black} \item 난 집중하려는 중이야. 
    \color{light-gray} I'm trying to focus.
  \color{black} \item 이사할까 생각 중이야.
    \color{light-gray} I'm thinking of moving.
  \color{black} \item 나 경제학 수강 중이야.
    \color{light-gray} I'm taking economics.
  \color{black} \item 네 사진들이 몹시 기대돼.
    \color{light-gray} I'm looking forward to your pictures.
  \color{black} \item 도와주실 수 있는지 궁금해서요.
    \color{light-gray} I was wondering if you could help me.
  \color{black} \item 내 말은 난 상관 안 한다는 거야.
    \color{light-gray} What I'm saying is I don't care.
  \color{black} \item 너 지금 나한테 거짓말했다고 말하는 거야?
    \color{light-gray} Are you telling me (that) you lied to me?
\end{enumerate}


\subsection{Pattern 008 - I'm getting... 점점 \texttildelow 해져}
\begin{itemize}
  \item \textbf{I'm getting} cold.
  \item \textbf{I'm getting} fat these days.
  \item \textbf{I'm getting} thinner.
  \item \textbf{I'm getting} better.
  \item \textbf{I'm getting} lazy for some reason.
\end{itemize}

\subsection{Pattern 009 - I'm trying to... 난 \texttildelow 하려는 중이야}
\begin{itemize}
  \item \textbf{I'm trying to} learn Japanese.
  \item \textbf{I'm trying to} practice English speaking.
  \item \textbf{I'm trying to} smile more.
\end{itemize}

\subsection{Pattern 010 - I'm thinking of... \texttildelow 할까 생각 중이야}
\begin{itemize}
  \item \textbf{I'm thinking of} quitting my job.
  \item \textbf{I'm thinking of} breaking up with him. (걔랑 헤어질까 생각중이야)
  \item \textbf{I'm thinking of} changing my hairstyle.
  \item \textbf{I'm thinking of} changing my major.
\end{itemize}

\subsection{Pattern 011 - I'm taking... 나 지금 \texttildelow 수강하고 있어 / 나 \texttildelow 수강할 거야}
\begin{itemize}
  \item \textbf{I'm taking} psychology. (psychology: 심리학)
  \item \textbf{I'm taking} sociology next semester. (sociology: 사회학)
  \item \textbf{I'm taking} Prof. Lee's chemistry class.
\end{itemize}

\subsection{Pattern 012 - I'm looking forward to... \texttildelow 이 너무 기대돼}
\begin{itemize}
  \item \textbf{I'm looking forward to} this weekend.
  \item \textbf{I'm looking forward to} the party.
  \item \textbf{I'm looking forward to} my blind date.(blind test: 소개팅)
  \item \textbf{I'm looking forward to} seeing my girlfriend.
  \item \textbf{I'm looking forward to} meeting you in person. (직접 뵐게 될 것이 무척 기대됩니다, in person: 직접의)
\end{itemize}

\subsection{Pattern 013 - I was wondering if... \texttildelow 한지 궁금해서요 / \texttildelow 할까 해서요}
\begin{itemize}
  \item \textbf{I was wondering if} I could come back later.
  \item \textbf{I was wondering if} you could help me.
  \item \textbf{I was wondering if} I could have a break.
  \item \textbf{I was wondering if} you could proofread this.(proofread: 교정보다)
  \item \textbf{I was wondering if} you could tell me the answer.
\end{itemize}

\subsection{Pattern 014 - What I'm saying is... \texttildelow 내 말은 \texttildelow 라는 거야}
\begin{itemize}
  \item \textbf{What I'm saying is} I don't love you.
  \item \textbf{What I'm saying is} I disagree.
  \item \textbf{What I'm saying is} it's not true.
  \item \textbf{What I'm saying is} I'm sorry.
  \item \textbf{What I'm saying is} he's not trustworthy.(trustworthy: 믿을 만한, 신뢰할 수 있는)
\end{itemize}

\subsection{Pattern 015 - Are you telling me (that)...? 너 지금 \texttildelow 라고 말하는 거야?}
\begin{itemize}
  \item \textbf{Are you telling me} you don't know?
  \item \textbf{Are you telling me} you didn't hear that?
  \item \textbf{Are you telling me} you didn't do it?
  \item \textbf{Are you telling me} you forgot?
  \item \textbf{Are you telling me} she stood you up?(stand \texttildelow up: ~을 바람맞히다)
\end{itemize}

\end{document}
