\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 13-Why}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 너 왜 나한테 거짓말한 거야?
    \color{light-gray} Why did you lie to me?
  \color{red} \item 넌 왜 그녀를 안 좋아해?
    \color{light-gray} Why don't you like her?
  \color{black} \item 너 왜 나한테 전화 안 한 거야?
    \color{light-gray} Why didn't you call me?
  \color{red} \item 넌 왜 그렇게 건망증이 심한 거야?
    \color{light-gray} Why are you so forgetful?
  \color{red} \item 너 왜 그렇게 못되게 구는 거야?
    \color{light-gray} Why are you being so mean?
  \color{black} \item 너 왜 일 안 하고 있어?
    \color{light-gray} Why aren't you working?
   \color{red} \item 왜 나중에 하면 안 되는 거야?
    \color{light-gray} Why can I do it later?
   \color{black} \item 내가 왜 너한테 말해야 하는 건데?
    \color{light-gray} Why should I tell you?
\end{enumerate}

\subsection{Pattern 086 - Why did you...? 왜 \texttildelow 한 거야?}
\begin{itemize}
  \item \textbf{Why did you} do that?
  \item \textbf{Why did you} agree?
  \item \textbf{Why did you} say that?
  \item \textbf{Why did you} break up?
  \item \textbf{Why did you} stay up so late last night?
\end{itemize}

\subsection{Pattern 087 - Why don't you ...? 넌 왜 \texttildelow 안 해?}
\begin{itemize}
  \item \textbf{Why don't you} listen to me?
  \item \textbf{Why don't you} like me?
  \item \textbf{Why don't you} have a boyfriend?
  \item \textbf{Why don't you} talk to Jihyun?
  \item \textbf{Why don't you} want kids?
\end{itemize}

\subsection{Pattern 088 - Why didn't you...? 왜 \texttildelow 안 한거야?}
\begin{itemize}
  \item \textbf{Why didn't you} say so?
  \item \textbf{Why didn't you} come to me?
  \item \textbf{Why didn't you} call me?
  \item \textbf{Why didn't you} wake me?
  \item \textbf{Why didn't you} tell me anything?
\end{itemize}

\subsection{Pattern 089 - Why are you so...? 왜 그렇게 \texttildelow 한 거야?}
\begin{itemize}
  \item \textbf{Why are you so} down?
  \item \textbf{Why are you so} depressed?
  \item \textbf{Why are you so} cheerful?
  \item \textbf{Why are you so} sweaty?(sweaty: 땀 투성이의)
  \item \textbf{Why are you so} naive?(naive: 순진한, 세상 물정을 모르는)
\end{itemize}

\subsection{Pattern 090 - Why are you being so ...? 왜 그렇게 \texttildelow 하게 구는 거야?}
\begin{itemize}
  \item \textbf{Why are you being so} childish?(childish: 유치한, 철없는)
  \item \textbf{Why are you being so} nice to me?
  \item \textbf{Why are you being so} mean today?(mean: 심술궂은)
  \item \textbf{Why are you being so} difficult?(difficult: 까다로운, 비협조적인)
  \item \textbf{Why are you being so} negative?
\end{itemize}

\subsection{Pattern 091 - Why aren't you -ing? 왜 \texttildelow 안 하고 있어?}
\begin{itemize}
  \item \textbf{Why aren't you} sleep\textbf{ing}?
  \item \textbf{Why aren't you} study\textbf{ing}?
  \item \textbf{Why aren't you} laugh\textbf{ing}?
  \item \textbf{Why aren't you} do\textbf{ing} your assignment?
  \item \textbf{Why aren't you} say\textbf{ing} anything?
\end{itemize}

\subsection{Pattern 092 - Why can't I...? 왜 \texttildelow 하면 안 되는 거야? / \texttildelow 이 왜 안되는 거지?}
\begin{itemize}
  \item \textbf{Why can't I} do this first?
  \item \textbf{Why can't I} go last?
  \item \textbf{Why can't I} print here?
  \item \textbf{Why can't I} leave now?
  \item \textbf{Why can't I} login?
\end{itemize}

\subsection{Pattern 093 - Why should I...? 내가 왜 \texttildelow 해야 하는 건데?}
\begin{itemize}
  \item \textbf{Why should I} apologize to him?
  \item \textbf{Why should I} listen to you?
  \item \textbf{Why should I} say sorry?
  \item \textbf{Why should I} care?
  \item \textbf{Why should I} help her?
\end{itemize}

\end{document}
