\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 06-It's...}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 그냥 감기야. (O)
    \color{light-gray} It's just a cold.
  \color{black} \item 잠잘 시간이야.
    \color{light-gray} It's time to go to bed.
  \color{black} \item 그게......, 내가 피곤해서 말이야.
    \color{light-gray} It's just (that) I'm tired.
  \color{black} \item 내가 길을 잃은 게 당연해.
    \color{light-gray} It's no wonder I'm lost.
  \color{black} \item 넌 좋은 여자인 것 같아.
    \color{light-gray} It seems like/that you're a nice girl.
  \color{black} \item 자고 있는 것도 아니잖아.
    \color{light-gray} It's not like you're sleeping.
\end{enumerate}

\subsection{Pattern 039 - It's just... 단지 \texttildelow 일 뿐이야 / 그냥 \texttildelow 야}
\begin{itemize}
  \item \textbf{It's just} a joke!
  \item \textbf{It's just} a cold.
  \item \textbf{It's just} a matter of time.(단지 시간문제야.)
  \item \textbf{It's just} a rumor.
\end{itemize}

\subsection{Pattern 040 - It's time to... \texttildelow 할 시간이야 / \texttildelow 할 때야}
\begin{itemize}
  \item \textbf{It's time to} go to bed.
  \item \textbf{It's time to} get up.
  \item \textbf{It's time to} call it a day.(이제 퇴근할 시간이야.)
  \item \textbf{It's time to} grow up.(이제 철 좀 들 때야.)
  \item \textbf{It's time to} stop bumming around.(이제 그만 빈둥댈 때야.)
\end{itemize}

\subsection{Pattern 041 - It's just (that)... 그게..., \texttildelow 라서 말이야}
\begin{itemize}
  \item \textbf{It's just (that)} he's not my type.
  \item \textbf{It's just} I don't feel up to it.
  \item \textbf{It's just} I'm exhausted.
  \item \textbf{It's just} I'm really stressed out.
  \item \textbf{It's just} I'm not interested in her.(그게......, 그녀에게 관심이 없어서 말이야.)
\end{itemize}

\subsection{Pattern 042 - It's no wonder (that)... \texttildelow 한 게 당연해 / \texttildelow 할 만해}
\begin{itemize}
  \item \textbf{It's no wonder} I was confused.(내가 헷갈린 게 당연해.)
  \item \textbf{It's no wonder} the movie was a hit.
  \item \textbf{It's no wonder} your skin's so perfect.
  \item \textbf{It's no wonder} she has no friends.
  \item \textbf{It's no wonder} nobody listens to him.
\end{itemize}

\subsection{Pattern 043 - It seems like/that... \texttildelow 한 것 같아}
\begin{itemize}
  \item \textbf{It seems that} you're mistaken.(오해하신 것 같은데요.)
  \item \textbf{It seems that} it's going to rain.
  \item \textbf{It seems like} you're a nice guy.
  \item \textbf{It seems like} he's hiding something.
  \item \textbf{It seems like} you always pick on me.
\end{itemize}

\subsection{Pattern 044 - It's not like... \texttildelow 한 것도 아니잖아}
\begin{itemize}
  \item \textbf{It's not like} he's perfect.
  \item \textbf{It's not like} you like me.
  \item \textbf{It's not like} you're feeling guilty.
  \item \textbf{It's not like} you're in love with Jinwoo.
  \item \textbf{It's not like} you care anyway.
\end{itemize}

\end{document}
