\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 07-Is it...?}
\subsection{Quiz}
\begin{enumerate}
  \color{black} \item 밖에 어두운가요?
    \color{light-gray} Is it dark outside?
  \color{red} \item 다시 시작할 수 있을까요?
    \color{light-gray} Is it possible to start over?
  \color{red} \item 나중에 전화드려도 될까요?
    \color{light-gray} Is it okay if I call you later?
  \color{red} \item 쟤 너무 착하지 않아?
    \color{light-gray} Isn't she so nice?
  \color{red} \item 이게 주문하신 거예요?
    \color{light-gray} Is this what you ordered?
  \color{black} \item 걔들이 헤어졌다는 게 사실이야?
    \color{light-gray} Is is true they broke up?
\end{enumerate}

\subsection{Pattern 045 - Is it...? \texttildelow 한가요? / \texttildelow  인가요?}
\begin{itemize}
  \item \textbf{Is it} dark outside?
  \item \textbf{Is it} cold today?
  \item \textbf{Is it} Friday today?
  \item \textbf{Is it} 3:30 yet?(아직 3시 반 안 됐어?)
  \item \textbf{Is it} over already?(벌써 끝났어?)
\end{itemize}

\subsection{Pattern 046 - Is it possible to...? \texttildelow 할 수 있을까요? / \texttildelow 이 가능할까?}
\begin{itemize}
  \item \textbf{Is it possible to} fix this today?
  \item \textbf{Is it possible to} use the internet here?
  \item \textbf{Is it possible to} start over?(다시 시작할 수 있을까요?)
  \item \textbf{Is it possible to} lose 3kgs in 10 days?
  \item \textbf{Is it possible to} stay another day?(하루 더 머물 수 있을까요?)
\end{itemize}

\subsection{Pattern 047 - Is it okay if...? \texttildelow 해도 될까요?}
\begin{itemize}
  \item \textbf{Is it okay if} I park here?
  \item \textbf{Is it okay if} I call you back later?
  \item \textbf{Is it okay if} I bring a friend?
  \item \textbf{Is it okay if} I hand this in tomorrow?
  \item \textbf{Is it okay if} I think about it first?
\end{itemize}

\subsection{Pattern 048 - Isn't + 주어 + 형용사? \texttildelow 이지 / \texttildelow 하지 않아?}
\begin{itemize}
  \item \textbf{Isn't} that guy hot?(저 남자 끝내주지 않아?)
  \item \textbf{Isn't} that too much?(그건 너무 많지 않아?)
  \item \textbf{Isn't} she gorgeous?(저 여자 너무 멋지지 않니?)
  \item \textbf{Isn't} this nice?
  \item \textbf{Isn't} she so mean?(쟤 정말 못됐지 않아?)
\end{itemize}

\subsection{Pattern 049 - Is this what...?... 이게 \texttildelow 한 거예요?}
\begin{itemize}
  \item \textbf{Is this what} you ordered?(이게 주문하신 건가요?)
  \item \textbf{Is this what} you wanted?
  \item \textbf{Is this what} you asked for?
  \item \textbf{Is this what} you're looking for?
  \item \textbf{Is this what} he was talking about?
\end{itemize}

\subsection{Pattern 050 - Is it true (that) ...? \texttildelow 한 것도 아니잖아}
\begin{itemize}
  \item \textbf{Is it true (that)} he failed?
  \item \textbf{Is it true (that)} Junghyun got fired?
  \item \textbf{Is it true (that)} they broke up?
  \item \textbf{Is it true} Hyunjoo dropped out?(현주가 학교 그만뒀다는 게 사실이야?)
  \item \textbf{Is it true} she had double eyelid surgery?(걔 쌍커풀 수술 했다는 게 사실이야?)
\end{itemize}


\end{document}
