\documentclass[11pt]{oblivoir}

\usepackage{textcomp} % \texttildelow
\usepackage{color} % \color{{color}}

\definecolor{light-gray}{gray}{0.9}

\begin{document}

\section{Unit 11-What}
\subsection{Quiz}
\begin{enumerate}
  \color{red} \item 만약에 내가 실수하면 어쩌지?
    \color{light-gray} What if I make a mistake?
  \color{red} \item 넌 왜 그런 말을 하니?(무엇이 네가 그런 말을 하게 만들었니?)
    \color{light-gray} What makes you say that?
  \color{red} \item 어쩐 일로 여기에 오셨나요?
    \color{light-gray} What brings you here?
  \color{black} \item 어떤 종류의 음악을 좋아해?
    \color{light-gray} What kind of music do you like?
  \color{red} \item 데이트 어땠어?
    \color{light-gray} What was your date like?
  \color{red} \item 모른다니 그게 무슨 말이야?
    \color{light-gray} What do you mean you don't know?
   \color{black} \item 네가 뭘 알아?
    \color{light-gray} What do you know?
\end{enumerate}

\subsection{Pattern 072 - What if...? 만약에 \texttildelow 하면 어쩌지?}
\begin{itemize}
  \item \textbf{What if} I mess up?(만약에 내가 망치면 어쩌지?)
  \item \textbf{What if} it rains tomorrow?
  \item \textbf{What if} I can't get it done today?(만약에 내가 오늘 다 못 끝내면 어쩌지?)
  \item \textbf{What if} I forget my lines?(line: 선, 줄; 대사)
  \item \textbf{What if} I'm late again?
\end{itemize}

\subsection{Pattern 073 - What makes you + 형용사/동사원형? 뭐가 널 \texttildelow 하게 만들어? / 왜 \texttildelow 하니?}
\begin{itemize}
  \item \textbf{What makes you} say that?(왜 그런 말을 해?)
  \item \textbf{What makes you} happy?
  \item \textbf{What makes you} so sure?(어떻게 그렇게 확신해?)
  \item \textbf{What makes you} suspect him?(suspect: 의심하다)
  \item \textbf{What makes you} think so?
\end{itemize}

\subsection{Pattern 074 - What brings you...? 어쩐 일로 \texttildelow 에 오셨나요?}
\begin{itemize}
  \item \textbf{What brings you} here?
  \item \textbf{What brings you} to Korea?
  \item \textbf{What brings you} here at this hour?
  \item \textbf{What brings you} all the way here?(어쩐 일로 여기까지 오셨나요? all the way: 줄곧; 여러 가지로; 완전히)
  \item \textbf{What brings you} to my neighborhood?(인근, 근처, 이웃)
\end{itemize}

\subsection{Pattern 075 - What kind of...? 어떤 종류의 \texttildelow ?}
\begin{itemize}
  \item \textbf{What kind of} music do you like?
  \item \textbf{What kind of} work do you do?(어떤 종류의 일을 하세요?)
  \item \textbf{What kind of} pasta do you like?
  \item \textbf{What kind of} job are you looking for?
  \item \textbf{What kind of} car do you want?
\end{itemize}

\subsection{Pattern 076 - What is/was... like? \texttildelow 어때? / \texttildelow 어땠어?}
\begin{itemize}
  \item \textbf{What is} your new boyfriend like?
  \item \textbf{What is} your new place like?
  \item \textbf{What is} the weather like over there?
  \item \textbf{What was} your first date like?
  \item \textbf{What was} your sister like as a child?
\end{itemize}

\subsection{Pattern 077 - What do you mean...? \texttildelow 라니 그게 무슨 말이야?}
\begin{itemize}
  \item \textbf{What do you mean} you don't know?
  \item \textbf{What do you mean} you can't come?
  \item \textbf{What do you mean} you didn't finish?
  \item \textbf{What do you mean} you forgot?
  \item \textbf{What do you mean} you quit?
\end{itemize}

\subsection{Pattern 078 - What do(es) \texttildelow know (about...)? \texttildelow가 (...에 대해) 뭘 알아?}
\begin{itemize}
  \item \textbf{What do} you \textbf{know}?(네가 뭘 알아?)
  \item \textbf{What do} you \textbf{know about} fashion?
  \item \textbf{What do} you \textbf{know about} life?
  \item \textbf{What does} she \textbf{know about} soccer?
  \item \textbf{What does} he \textbf{know about} trust? 
\end{itemize}

\end{document}
